\EVOSUITE at the SBST 2018 Tool Competition

### 2018-03-07 papers/sbst18/paper_sbst18.tex
andrea
Minor edits

@@

%------------------------------------------------------------------------- 
\section{Introduction}
The annual unit test generation competition aims to drive and evaluate
progress on unit test generation tools. In the 6th instance of the
competition at the International Workshop on Search-Based Software
Testing (SBST) 2018, two tools, \EVOSUITE and \JTEXPERT\TODO{confirm},
competed on a set of 59 open-source Java classes. Two other tools,
\RANDOOP and \TT, and existing open-source test suites were used as
baseline. This paper describes the results obtained by the \EVOSUITE
test generation tool~\cite{FrA11c} in this competition. Details about
the procedure of the competition, the technical framework, and the
benchmark classes can be found in~\cite{sbst18competition}.  In this
competition, \EVOSUITE achieved an overall score of \TOTALPOINTS,
which was the highest among the competing and baseline
tools\TODO{confirm baseline}.

@@

\EVOSUITE has a longstanding record of success at the unit testing
tool competition, having ranked second the third edition of the
competition~\cite{evosuiteAtSbst2015} and first in all the other
editions~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013,evosuiteAtSbst2016,evosuiteAtSbst2017}.

@@

The configuration of \EVOSUITE for the competition is largely based on
its default values, since these have been tuned
extensively~\cite{arcuri2013parameter}. We used the default set of
coverage criteria~\cite{rojas2015combining} (e.g., line coverage,
branch coverage, branch coverage by direct method invocation, weak
mutation testing, output coverage, exception coverage). \EVOSUITE uses
an archive of solutions~\cite{emse_archive} to keep the search focused
on uncovered goals, iteratively discarding covered goals and storing
the tests that covered them. After a certain percentage of the search
budget has passed and with a certain probability, \EVOSUITE starts
using mock objects (relying on Mockito) instead of actual class
instances~\cite{ICST_Mocking17}; only branches that cannot be covered
without mocks lead to tests with mock objects. As in the previous
instance of the competition, we continue to use frequency-based
weighted constants for seeding~\cite{sakti2015instance} and support
Java Enterprise Edition features~\cite{arcuri2016java}. \TODO{any
  other noteworthy change?} \EVOSUITE is being actively developed,
therefore several improvements and bug fixes were applied since the
last instance of the competition, in particular in relation to
non-determinism and flaky tests~\cite{arcuri2014automated}.

@@

%\noindent
\textbf{Acknowledgments:} Many thanks to all the contributors to \EVOSUITE.
This project has been funded by the EPSRC
project ``GREATEST'' (EP/N023978/1), and by the National Research
Fund, Luxembourg (FNR/P10/03)\TODO{remove?}.

>>>>

\author{Andrea Arcuri}
\affiliation{%
  \institution{Westerdals Oslo ACT}
  \city{Oslo}
  \country{Norway}
}
\email{arcand@westerdals.no}

@@

%------------------------------------------------------------------------- 
\section{Introduction}
The annual unit test generation competition aims to drive and evaluate
progress on unit test generation tools. In the 6th instance of the
competition at the International Workshop on Search-Based Software
Testing (SBST) 2018, several JUnit test generation tools
%two tools, \EVOSUITE and \JTEXPERT\TODO{confirm},
competed on a set of 59 open-source Java classes, and 
% Two other tools,
%\RANDOOP and \TT, and 
existing open-source test suites were used as
baseline. This paper describes the results obtained by the \EVOSUITE
test generation tool~\cite{FrA11c} in this competition. Details about
the procedure of the competition, the technical framework, and the
benchmark classes can be found in~\cite{sbst18competition}.  In this
competition, \EVOSUITE achieved an overall score of \TOTALPOINTS,
which was the highest among the competing and baseline
tools.

@@

\EVOSUITE has a longstanding record of success at the unit testing
tool competition, having ranked second in the third edition of the
competition~\cite{evosuiteAtSbst2015} and first in all the other
editions~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013,evosuiteAtSbst2016,evosuiteAtSbst2017}.

@@

The configuration of \EVOSUITE for the 2018 competition is largely
based on its default values, since these have been tuned
extensively~\cite{arcuri2013parameter}. We used the default set of
coverage criteria~\cite{rojas2015combining} (e.g., line coverage,
branch coverage, branch coverage by direct method invocation, weak
mutation testing, output coverage, exception coverage). \EVOSUITE uses
an archive of solutions~\cite{emse_archive} to keep the search focused
on uncovered goals, iteratively discarding covered goals and storing
the tests that covered them. After a certain percentage of the search
budget has passed and with a certain probability, \EVOSUITE starts
using mock objects (relying on Mockito) instead of actual class
instances~\cite{ICST_Mocking17} for dependencies; only branches that
cannot be covered without mocks lead to tests with mock objects. As in
the previous instance of the competition, we continue to use
frequency-based weighted constants for
seeding~\cite{sakti2015instance} and support Java Enterprise Edition
features~\cite{arcuri2016java}. %\TODO{any other noteworthy change?} No.
\EVOSUITE is actively maintained, therefore several bug fixes and
minor improvements have been applied since the last instance of the
competition, in particular in relation to non-determinism and flaky
tests~\cite{arcuri2014automated}, as well as new types of test
assertions (e.g., related to arrays and standard contained classes).

@@

%\noindent
\textbf{Acknowledgments:} Many thanks to all the contributors to \EVOSUITE.
This project has been funded by the EPSRC
project ``GREATEST'' (EP/N023978/1).
%, and by the National Research
%Fund, Luxembourg (FNR/P10/03)\TODO{remove?}.
